\textbf{Data analysis for maximum-precision radial-velocity mesurement}

### 2018-07-18 paper/paper.tex
new title and abstract

\documentclass[modern]{aastex61}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[sort&compress]{natbib}
\usepackage[hang,flushmargin]{footmisc}

@@

% text macros
\newcommand{\sectionname}{Section}
\newcommand{\todo}[1]{\textcolor{red}{#1}}  % gotta have \usepackage{xcolor} in main doc or this won't work
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\foreign}[1]{\textsl{#1}}
\newcommand{\HARPS}{\project{\acronym{HARPS}}}
\newcommand{\HIRES}{\project{\acronym{HIRES}}}
\newcommand{\RV}{\acronym{RV}}
\newcommand{\CRLB}{\acronym{CRLB}}

\setlength{\parindent}{1.4em} % trust in Hogg
\shorttitle{achieving maximum radial-velocity precision}
\shortauthors{bedell and hogg}

@@

\title{Achieving maximum possible precision on stellar radial-velocity measurements in multi-epoch spectroscopy}

@@

\begin{abstract}\noindent
% context
Extremely precise stellar radial velocity (\RV) measurements are a foundational tool in the field of exoplanets, with hundreds of planets discovered by the Doppler method to date and about a dozen high-resolution spectrographs around the world dedicated to the search.
Despite the importance of these observations, the detailed computational methods used to extract $\ms$-level \RV s from stellar spectra remain largely unstandardized and unpublished.
% aims
In this work, we look at sensible approaches to extracting \RV s from a data set of extracted spectra and compare their efficiencies by testing on a segment of realistic model spectrum, with the goal of identifying methods that have the possibility of saturating the information-theoretic Cram\'er--Rao bound (\CRLB) on measurement precision.
% methods
We consider cross-correlations (and, equivalently, maximum-likelihood optimizations) of the data with generalized (weighted) binary masks, synthetic spectra (from, say, stellar models), and data-driven templates constructed from the data themselves.
We also consider the possibility that there are low-amplitude, unknown telluric absorptions (micro-tellurics) affecting the spectrum, and continuum-normalization problems, and measure improvements that flow from modeling those also in a data-driven way.
% results
We find that of all methods, only cross-correlation with an iteratively built data-driven template comes close to saturating the \CRLB.
We find that if there are micro-tellurics, they can be captured by a data-driven model.
We predict that simultaneously fitting data-driven models of the stellar spectrum and telluric contributions at all observational epochs will improve the \RV\ precision of \HARPS\ to substantially better than $1\,\ms$.
\end{abstract}

@@

>>>>

\documentclass[modern]{aastex62}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[sort&compress]{natbib}
\usepackage[hang,flushmargin]{footmisc}

@@

% text macros
\newcommand{\documentname}{\textsl{Article}}
\newcommand{\sectionname}{Section}
\newcommand{\todo}[1]{\textcolor{red}{#1}}  % gotta have \usepackage{xcolor} in main doc or this won't work
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\foreign}[1]{\textsl{#1}}
\newcommand{\HARPS}{\project{\acronym{HARPS}}}
\newcommand{\HIRES}{\project{\acronym{HIRES}}}
\newcommand{\RV}{\acronym{RV}}
\newcommand{\CRLB}{\acronym{CRLB}}

\setlength{\parindent}{1.4em} % trust in Hogg
\shorttitle{data analysis for radial-velocity measurement}
\shortauthors{bedell and hogg}

@@

\title{\textbf{Data analysis for maximum-precision radial-velocity mesurement}}

@@

\begin{abstract}\noindent
% context
Extremely precise stellar radial velocity (\RV) measurements are a
foundational tool in the field of exoplanets, with hundreds of planets
discovered by the Doppler method to date and many high-resolution
spectrographs around the world dedicated to search and
characterization.
Current observations are delivering \RV\ measurements at $\ms$
precision, while it is thought that some hardware systems ought to be
delivering data capable of even higher precisions.
% aims
The question arises: Is there any precision loss in current
data-analysis methods?
That is, what data-analysis methods deliver \RV\ measurements that
saturate the information-theoretic bound on precision---the
Cram\'er--Rao bound (\CRLB)---given an extracted spectrum (and
associated uncertainties) from a spectrograph?
% methods
We consider cross-correlation with a binary mask, a smoothed (or
Gaussian-fit) cross-correlation with a binary mask, and
cross-correlation with a stellar template.
We consider both theoretically generated and data-driven templates,
and look at some methods for data-driven telluric removal.
% results
As expected, we find that cross-correlation with a correct stellar
template produces \RV\ measurements that saturate the \CRLB.
We find that pure cross-correlation with a binary mask under-performs,
but the standard practice of post-processing the binary-mask result
with a Gaussian fit does saturate the \CRLB, when the binary mask is
``correct'' in a certain sense.
As the template or mask becomes incorrect, \RV\ precision suffers.
Most importantly, we find that using the data themselves to generate
the stellar template does not cost any significant information; that
is, a data-driven template will be correct enough to saturate the
\CRLB, provided that there are multiple epochs of observations and the
star does not vary substantially between epochs.
As a side note, we find that tiny telluric features can affect \RV\ precision
substantially, but that they can be modeled and removed by a data-driven
method, provided that there is sufficient barycentric velocity variation.
\end{abstract}

@@

\todo{needs reduction in scope, perhaps?}
